---
title: "R and SQL"
output: html_document
---

# Jhalak Das 
## Week 3 Assignment

**
In this project, 
    I created a SQL instance in GCP, 
    connect it to MYSQL Workbench,
    created a database and tree separate tables in that database,
    imported necessary r libraries, configured DSN 
    and connected the database through odbc
    Also ran few SQL custom queries directly from r.
    Finally, uploaded the code to my github repository.
**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import libraries
```{r}
library(RODBC)
library(dplyr)
library(DBI)
library(odbc)
```

## Display all three tables
```{r}
conn1 <- odbcConnect("MySQL_DSN")
sqlQuery(conn1, 'SELECT * FROM usertbl')
sqlQuery(conn1, 'SELECT * FROM movietbl')
sqlQuery(conn1, 'SELECT * FROM reviewtbl')
```

## Join data from all table 
```{r}
sqlQuery(conn1, 
"SELECT M.title As 'Title', U.full_name As 'User',
R.rating As 'Rating'
FROM movietbl AS M
JOIN reviewtbl AS R
ON M.movie_id = R.movie_id
JOIN usertbl AS U
ON U.user_id = R.user_id;"
)
```

## Custom Query based on single user
```{r}
sqlQuery(conn1, "SELECT 
M.title As 'Title',
U.full_name As 'User',
R.rating As 'Rating'
FROM movietbl AS M
JOIN reviewtbl AS R
ON M.movie_id = R.movie_id
JOIN usertbl AS U
ON U.user_id = R.user_id
WHERE U.user_id = 1;")
```


## Custom query based on certain rating
```{r}
sqlQuery(conn1, "SELECT 
M.title As 'Title',
U.full_name As 'User',
R.rating As 'Rating'
FROM movietbl AS M
JOIN reviewtbl AS R
ON M.movie_id = R.movie_id
JOIN usertbl AS U
ON U.user_id = R.user_id
WHERE R.rating = 5;")
```


## Another way to connect to database created in MySQL
```{r}
conn2 <- dbConnect(odbc :: odbc(), "MySQL_DSN")

# List tables
dbListTables(conn2)

# List columns of certain table
dbListFields(conn2, "movietbl")
```

## Import tables as df
```{r}
movietbl <- tbl(conn2, "movietbl")
movietbl_df <- collect(movietbl)
movietbl_df 

usertbl <- tbl(conn2, "usertbl")
usertbl_df <- collect(usertbl)
usertbl_df 

reviewtbl <- tbl(conn2, "reviewtbl")
reviewtbl_df <- collect(reviewtbl)
reviewtbl
```


